---
title: "Wearable Technology for MS: Review Search Strategy"
author: "Tim Woelfle"
date: "18/03/2021"
output:
  html_notebook:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
---

# Search term

All searches performed on 18.03.2021. Term: 

"multiple sclerosis" AND ("smartphone" OR "smartphones" OR "smartwatch" OR "smartwatches" OR "wearable" OR "wearables" OR "biosensor" OR "biosensors" OR "digital biomarker" OR "digital biomarkers" OR "accelerometer" OR "accelerometers" OR "accelerometry" OR "gyroscope" OR "gyroscopes" OR "inertial motion unit" OR "IMU")

# Pubmed (354)

```{r}
suppressPackageStartupMessages(library(data.table))
suppressPackageStartupMessages(library(VennDiagram))

pubmed = fread("21-03-18 Pubmed 354 search results.csv", data.table = F)
pubmed[pubmed$DOI == '', 'DOI'] = NA
pubmed$DOI = toupper(pubmed$DOI)

table(pubmed$Type, hasDOI=!is.na(pubmed$DOI))
hist(pubmed$Year)
```

# Scopus (497)

```{r}
# scop1 = read.csv("21-03-18 Scopus 1975-2014.csv", stringsAsFactors = F)
# scop2 = read.csv("21-03-18 Scopus 2015-2018.csv", stringsAsFactors = F)
# scop3 = read.csv("21-03-18 Scopus 2019-2021.csv", stringsAsFactors = F)
# scopus = rbind(scop1,scop2,scop3)
# write.csv(scopus, "21-03-18 Scopus 497 search results.csv", row.names = F)

scopus = fread("21-03-18 Scopus 497 search results.csv", data.table = F)
scopus[scopus$DOI == '', 'DOI'] = NA
scopus$DOI = toupper(scopus$DOI)

table(scopus$Type, hasDOI=!is.na(scopus$DOI))
hist(scopus$Year)
```

# Embase (727)

```{r}
embase = fread("21-03-18 Embase 727 search results.csv", data.table=F)
embase[embase$DOI == '', 'DOI'] = NA
embase$DOI = toupper(embase$DOI)

table(embase$`Publication Type`, hasDOI=!is.na(embase$DOI))
hist(embase$`Publication Year`)
```

# Web of Science (510)

```{r}
wos = fread("21-03-18 WoS 510 search results.csv", data.table=F)
wos[wos$DOI == '', 'DOI'] = NA
wos$DOI = toupper(wos$DOI)

table(wos$`Document Type`, hasDOI=!is.na(wos$DOI))
hist(wos$`Publication Year`)
```

# DOI Overlap

```{r, fig.width=8, fig.height=6}
grid.newpage()
grid.draw(venn.diagram(sapply(list(Embase=embase$DOI, WoS=wos$DOI, PubMed=pubmed$DOI, Scopus=scopus$DOI), na.omit), NULL))
```

# Concat

```{r}
# Embase is the only database in which DOIs are not unique (presumably e.g. because of conference abstracts often published under one summary DOI)
table(table(pubmed$DOI))
table(table(scopus$DOI))
table(table(embase$DOI))
table(table(wos$DOI))

pubmed$database = "PubMed"
scopus$database = "Scopus"
embase$database = "Embase"
wos$database = "WoS"

# First combine PubMed and Scopus
pubmed_scopus = rbind(
  scopus[, c("Authors", "Title", "Source", "Year", "Abstract", "Type", "DOI", "ArticleURL", "database")],
  pubmed[is.na(pubmed$DOI) | !pubmed$DOI %in% scopus$DOI, c("Authors", "Title", "Source", "Year", "Abstract", "Type", "DOI", "ArticleURL", "database")]
)
colnames(pubmed_scopus) = c("Authors", "Article Title", "Source Title", "Publication Year", "Abstract", "Document Type", "DOI", "UT (Unique WOS ID)", "database")

# Then with WoS
pubmed_scopus_wos = rbind(
  wos[, c("Authors", "Article Title", "Source Title", "Publication Year", "Abstract", "Document Type", "DOI", "UT (Unique WOS ID)", "database")],
  pubmed_scopus[is.na(pubmed_scopus$DOI) | !pubmed_scopus$DOI %in% wos$DOI,]
)
colnames(pubmed_scopus_wos) = c("Author Names", "Title", "Source title", "Publication Year", "Abstract", "Publication Type", "DOI", "Open URL Link", "database")

# Sanity check for pubmed_scopus_wos
nrow(pubmed_scopus_wos) == length(unique(c(pubmed$DOI, scopus$DOI, wos$DOI)))-1 + sum(is.na(c(pubmed$DOI, scopus$DOI, wos$DOI)))

# And finally merge with Embase
merged = rbind(
  embase[, c("Author Names", "Title", "Source title", "Publication Year", "Abstract", "Publication Type", "DOI", "Open URL Link", "database")],
  pubmed_scopus_wos[is.na(pubmed_scopus_wos$DOI) | !pubmed_scopus_wos$DOI %in% embase$DOI,]
)

# Remove Title duplicates
length(unique(gsub("\\.$","",tolower(merged$Title)))) # Number of unique titles (irrespective of case and trailing period)
merged = merged[order(merged$`Publication Year`, merged$Title, merged$Abstract, merged$DOI),]
merged = merged[!duplicated(gsub("\\.$","",tolower(merged$Title))),]

write.csv(merged, "21-03-19 merged 959.csv", row.names = F)
```

